\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-24 Latex/paper.tex
# add new appendix

\begin{example}
In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$. In the case of a Hull-White model, we have that
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore (\ref{cms_first_order_convexity}) is equal to
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
\end{equation*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order_1.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta^{2}(u,x_0,y_0) du
\end{equation*}
Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
\begin{equation}\label{approximation_x_t_a}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation}
With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(0,\bar{x}_0(T_a), \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
\end{equation*}
where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
\begin{align*}
X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
\end{align*} 
Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{align*}
\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$

\begin{equation}\label{approsimation_E_s_x_t}
\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
\end{equation}

\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{T_a}\right)$}
Following the same procedure as before, we have that
\begin{equation*}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation*}
and therefore (see (\ref{approsimation_E_s_x_t}))
\begin{equation}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
\begin{equation}\label{approsimation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
\end{equation}

\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$}
It is easy to show that the dynamic of the bond under HJM assumption is
\begin{equation}
\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
\end{equation}
Therefore, if we apply Itô formula we have that 
\begin{equation}\label{annuity_spot_dynamic}
\frac{d01(t,T_a,T_b)}{01(t,T_a,T_b)} = r_t dt - \sigma_{01}(t,T_a,T_b)dW^{\mathbb{Q}}_t
\end{equation}
where 
\begin{equation} \label{annuity_vol}
\sigma_{01}(t,T_a,T_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,T_i) \nu(t,T_i)}{01(t,T_a,T_b)}.
\end{equation}
From (\ref{annuity_spot_dynamic}) and using the Girsanov's theorem that 
\begin{equation*}
dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,T_a,T_b)dt. 
\end{equation*}
We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
\begin{equation}
\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
\end{equation}
with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,T_a,T_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the last approximation we have that
\begin{align}
x_t &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t}  \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
&=  \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du  + \nonumber \\ 
& \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
\end{align}
Therefore, we have that
\begin{align}
\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du \nonumber \\ 
+ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du
\end{align}

\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{T_a} \right)$}

>>>>

\begin{example}
In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$. In the case of a Hull-White model, we have that
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore (\ref{cms_first_order_convexity}) is equal to
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
\end{equation*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.007$ and $k=0.0007$

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure} 
\end{example}

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}} 
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta^{2}(u,x_0,y_0) du
\end{equation*}
Therefore, if we define 
\begin{equation}\label{y_t_approximation}
\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0), 
\end{equation}
we have that
\begin{equation}\label{approximation_x_t_a}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation}
With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(0,\bar{x}_0(T_a), \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
\end{equation*}
where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
\begin{align*}
X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
\end{align*} 
Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{align*}
\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$

\begin{equation}\label{approximation_E_s_x_t}
\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
\end{equation}

\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{T_a}\right)$}
Following the same procedure as before, we have that
\begin{equation}\label{approximation_x_t_a}
X_{T_a} \approx \bar{X}_{T_a}:= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation}
and therefore (see (\ref{approsimation_E_s_x_t}))
\begin{equation}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
\begin{equation}\label{approsimation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
\end{equation}

\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$}
It is easy to show that the dynamic of the bond under HJM assumption is
\begin{equation}
\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
\end{equation}
Therefore, if we apply Itô formula we have that 
\begin{equation}\label{annuity_spot_dynamic}
\frac{d01(t,T_a,T_b)}{01(t,T_a,T_b)} = r_t dt - \sigma_{01}(t,T_a,T_b)dW^{\mathbb{Q}}_t
\end{equation}
where 
\begin{equation} \label{annuity_vol}
\sigma_{01}(t,T_a,T_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,T_i) \nu(t,T_i)}{01(t,T_a,T_b)}.
\end{equation}
From (\ref{annuity_spot_dynamic}) and using the Girsanov's theorem that 
\begin{equation*}
dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,T_a,T_b)dt. 
\end{equation*}
We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
\begin{equation}\label{approximation_o1_vol}
\sigma_{01}(t,T_a,T_b) \approx \bar{\sigma}_{0,1}(t,T_a,T_b):= \sum_{i=a+1}^{b} w_i \nu(t,T_i)
\end{equation}
with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,T_a,T_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the last approximation we have that
\begin{align}
x_t &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t}  \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
&=  \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du  + \nonumber \\ 
& \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
\end{align}
Therefore, we have that
\begin{align}
\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du \nonumber \\ 
+ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du
\end{align}

\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{T_a} \right)$}
Let us to remember that $\nu(t,T_i)=h(t,x_t,y_t) \frac{G(t,T_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$. Then, we can do the next approximation 
$$
\nu(t,T_i) \approx \nu(t,T_i, \bar{x}_t, \bar{y}_t),
$$ 
therefore 
\begin{equation*}
D_s \nu(t,T_i) \approx  \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,T_i)}{\beta_{t,k}}
\end{equation*}
A cosequence of the last approximation is that 
\begin{equation}
D_s \sigma_{0,1}(t,T_a,T_b) \approx  D_s \bar{x}_t \mu(t,T_a,T_b)
\end{equation}
Where 
$$
\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) \frac{G(t,T_i)}{\beta_{t,k}}.
$$

Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
\begin{align*}
\bar{x}_{T_a} &\approx  \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\sigma}_{01}(u,T_a,T_b) du \nonumber \\\
&+  \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}
\end{align*}
Therefore
\begin{equation*}
D_s \bar{x}_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}^{01}(s,T_a)
\end{equation*}
where
\begin{align*}
\bar{M}^{01}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right)\right) \\
&\cdot\exp\left(\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}^{01}}_u \right)
\end{align*}
with $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Then

\begin{equation}\label{approximation_E_01_s_x_t}
\mathbb{E}^{01}_s\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right).
\end{equation}
